\documentclass[reqno]{amsart} 
\usepackage{amssymb,latexsym,amsmath,amscd,graphicx,setspace,amsthm,verbatim}
\usepackage[margin = 3 cm]{geometry}


\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{question}{Question}
\newtheorem{problem}{Problem}
      
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newenvironment{solution}{\paragraph{\emph{Solution}.}}{\hfill$\square$}


\newenvironment{solution1}{\paragraph{\emph{Solution $1$}.}}{\hfill$\square$}
\newenvironment{solution2}{\paragraph{\emph{Solution $2$}.}}{\hfill$\square$}
\newenvironment{solution3}{\paragraph{\emph{Solution $3$}.}}{\hfill$\square$}

\begin{document} 

\title[Homework 10]{Homework 10}

\date{\today} 
\maketitle 


\begin{problem}
Both the dihedral group $D_{8}$ and the quaternion group $Q_{8}$ have cardinality $8$.  Are they isomorphic to one another?  If yes, exhibit an isomorphism.  If not, explain why.
\end{problem}
\begin{proof}

\end{proof}

\begin{problem}
Both the dihedral group $D_{6}$ and the permutation group $S_{3}$ have cardinality $6$.  Are they isomorphic to one another.  If yes, exhibit an isomorphism.  If not, explain why.  (Hint:  Label the vertices of the triangle using numbers $1,2,3$...)
\end{problem}


For the following problem, you might want to review the cartesian products of two groups.
\begin{problem}
Consider the abelian group
$$G = \mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/4\mathbb{Z}, $$
and the element $g = (\bar{1},\bar{2}) \in G$.  (I use the bar notation to denote an integer modulo $n$ for some $n$ which should be understood from the context...)
\begin{enumerate}
\item What is ${\rm Ord}(g)$?
\item What is $H = \langle g\rangle$?
\item Enumerate all the elements in $G/H$.
\item What is $(G:H)$?
\end{enumerate}
\end{problem}
\begin{solution}

\end{solution}

\begin{problem}
Consider the group morphism
$$\pi_{2}: \mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/4\mathbb{Z} \longrightarrow \mathbb{Z}/4\mathbb{Z}$$
given by 
$$(\bar{a},\bar{b}) \mapsto \pi_{2}(\bar{a},\bar{b}) = \bar{b}.$$
\begin{enumerate}
\item What is ${\rm ker}(\pi_{2})$?
\item Let $H = {\rm ker}(\pi_{2})$.  Enumerate all the elements in $G/H$, where $G=  \mathbb{Z}/2\mathbb{Z} \times \mathbb{Z}/4\mathbb{Z}$.
\end{enumerate}
\end{problem}
\begin{solution}

\end{solution}

\begin{problem}
Consider $S_{4}$ and let $\sigma = (2 \, 3 \, 4 \, 1) \in S_{4}$.  Let $H = \langle (2 \, 3 \, 4 \, 1) \rangle $.
\begin{enumerate}
\item What is ${\rm Ord}(g)$?
\item What is $|H|$?
\item What is $(G:H)$?
\item Find a representative for each left coset.
\end{enumerate}
\end{problem}









































\end{document} 

