\documentclass[reqno]{amsart} 
\usepackage{amssymb,latexsym,amsmath,amscd,graphicx,setspace,amsthm,verbatim}
\usepackage[margin = 3 cm]{geometry}


\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{question}{Question}
\newtheorem{problem}{Problem}
      
\theoremstyle{definition}
\newtheorem{definition}{Definition}

\newenvironment{solution}{\paragraph{\emph{Solution}.}}{\hfill$\square$}


\newenvironment{solution1}{\paragraph{\emph{Solution $1$}.}}{\hfill$\square$}
\newenvironment{solution2}{\paragraph{\emph{Solution $2$}.}}{\hfill$\square$}
\newenvironment{solution3}{\paragraph{\emph{Solution $3$}.}}{\hfill$\square$}

\begin{document} 

\title[Homework 6]{Homework 6}

\date{\today} 
\maketitle 

\begin{problem}
Let $G_{1}$ and $G_{2}$ be two groups and let $f:G_{1} \longrightarrow G_{2}$ be a group isomorphism.  Since $f$ is an isomorphism, it is in particular a bijection, and thus one can talk about its inverse $f^{-1}:G_{2} \longrightarrow G_{1}$.  Show that $f^{-1}$ is a group isomorphism.
\end{problem}
\begin{proof}

\end{proof}

\begin{problem}
Let $G_{1}$ and $G_{2}$ be two groups and assume that $f:G_{1} \longrightarrow G_{2}$ is an isomorphism.  
\begin{enumerate}
\item Show that $G_{1}$ is abelian if and only if $G_{2}$ is abelian.
\item If $f$ is only a group morphism and not an isomorphism, then is this statement true?  If yes, prove it.  Otherwise, give a counter-example. (Hint:  Think about all the examples of group homomorphism we went over in class...)
\end{enumerate}
\end{problem}
\begin{proof}

\end{proof}

\begin{problem}
Consider the following set of matrices
$$X = \left\{\begin{pmatrix} 1 & m \\ 0 & 1\end{pmatrix} \Big| \,m \in \mathbb{Z}\right\} \subseteq {\rm GL}(2,\mathbb{R})$$
with the binary operation being multiplication of matrices.  
\begin{enumerate}
\item Show that $X \le {\rm GL}(2,\mathbb{R})$.  Is $X$ an abelian group?
\item Consider now the function $f:\mathbb{Z} \longrightarrow X$ defined via 
$$m \mapsto f(m) = \begin{pmatrix}1 & m \\ 0 & 1 \end{pmatrix}. $$
Show that $f$ is an isomorphism of groups.
\end{enumerate}
\end{problem}
\begin{proof}

\end{proof}


\begin{problem}
If there exists a group isomorphism from $G_{1}$ to $G_{2}$, then we write 
$$G_{1} \simeq G_{2}.$$  
Show that this relation on the set of all groups is an equivalence relation.
\end{problem}
\begin{proof}

\end{proof}
















\end{document} 


